Numerical analysis of the influence of magnetic field waveforms on the performance of active magnetic regenerators

### 2019-09-19 PaperMagneticProfiles_JBSMSE.tex
Comment on evaluation of stainless steel and air thermophysical properties.
Update power figure with different colors and correct filename.

The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, with the same trends as for the cooling capacity; however, in this case  the rectified cosine profile yields better results for small to medium values of utilization. This is due to \textcolor{black}{a} lower pumping power, as the mass flow rate for the cosine profile is slightly higher, but also flows for a shorter period of time. \textcolor{black}{Since} in this region the cooling capacity for the RC profile can be close to or higher than the \textcolor{black}{IT} profile (cf. Fig.~\autoref{fig:comp_min}), the coefficient of performance becomes higher for the rectified cosine profile.

@@

@@

In addition, \textcolor{black}{in the present study}, an air gap clearance thickness was set at $h\ped{air} = \SI{1}{\mm}$. This value \textcolor{black}{gave rise to a} peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.

>>>>

The same analysis, but in terms of the coeficient of performance, is shown in \autoref{fig:cos_ins_cop}, where it can be seen that the instantaneous profile yields better results for medium to high levels of utilization. This is due to some phenomena shown in \autoref{fig:cos_ins_w} for a fixed utilization of 0.6: the magnetic power only change between profiles due to variations in cooling capacity; the valve power is higher for the IT profile since the valves must remain open for longer periods; but the proportional increase in pumping power, due to larger flow rate, is even higher (than the change in valve power).

@@

\begin{figure}[!ht]
  \centering
  \includegraphics[width=10cm]{W_B_comp_f_1_Phi_60_same_minimum}
  \caption{Power contributions as functions of the average high magnetic field, for a utilization of 0.6. \textcolor{black}{``IT''}: instantaneous (blow fraction of \SI{100}{\percent}); ``RC'': rectified cosine  (blow fraction of \SI{60}{\percent}).}
  \label{fig:cos_ins_w}
\end{figure}

@@

In addition, \textcolor{black}{in the present study}, an air gap clearance thickness was set at $h\ped{air} = \SI{1}{\mm}$. This value \textcolor{black}{gave rise to a} peak in cooling capacity due to the compromise between minimizing losses and maximizing the magnetocaloric mass.  The thermophysical properties of stainless steel and air were also obtained with interpolation of tables exported by the EES software \cite{bib:klein13-ees}.
